Loneliness

### 2023-01-06 docsrc/documentation/notebooks/loneliness.Rmd
get all current module templates with better formatting in taskbar.
update naming in some transition modules. improve website some more

# Loneliness

@@

## Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/loneliness_clm_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

## References

>>>>

## Loneliness

@@

```{r loneliness_data}
discrete_barplot("loneliness")
```

### Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("../../../data/transitions/test/loneliness_clm_2018_2019.rds", "loneliness_next") 
clm_output("../../../data/transitions/test/loneliness_clm_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

### References
